%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{PRASIDHI SASMAL} \\[7.5pt]
\href{mailto:prasidhisasmal14@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ prasidhisasmal14@gmail.com} \ $|$ \ 
\href{tel:+917855044833}{\raisebox{-0.05\height}\faMobile \ 7855044833} \ $|$ \ 
\raisebox{-0.05\height}\faMapMarker \ Berhampur, India \\[4pt]
\href{https://github.com/prasidhi55}{\raisebox{-0.05\height}\faGithub \ prasidhi55} \ $|$ \ 
\href{https://www.linkedin.com/in/prasidhi-sasmal-31328737a}{\raisebox{-0.05\height}\faLinkedin \ prasidhi-sasmal-31328737a} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Profile Summary}
Committed ECE student with practical experience in Arduino-driven embedded projects, MATLAB simulations, and Verilog-based digital design. Passionately interested in research and innovation, with a strong focus on VLSI, IoT systems, and core electronics. Seeking a research internship opportunity to contribute to semiconductor and embedded system projects while applying analytical and problem-solving skills.

%Experience
\section{Core Competencies}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    \item Python
    \item Data Structures using C Programming
    \item MATLAB
    \item Leadership Skills
    \item Analytical Skills
\end{itemize}
  
%Projects
\section{Project Details}

\begin{joblong}{SMART PILL BOX (GitHub)}{Oct 2025 -- Jan 2026}
\item The Smart Pill Box is an IoT-driven healthcare system bridging hardware and software. Utilizing a sensor-equipped box and a Flutter app synced via Firebase, it tracks real-time medication adherence. This closed-loop system triggers alerts and logs intake, demonstrating integration of embedded systems and mobile application architecture to improve patient outcomes.
\end{joblong}

\begin{joblong}{FIRE FIGHTING ROBOT}{Sep 2025 -- Dec 2025}
\item A Fire Fighting Robot is an automated robotic system designed to detect and extinguish fire using sensors and a water pump mechanism. It uses an Arduino microcontroller to control movement and process signals from flame sensors. The robot moves toward the fire source and sprays water automatically to reduce fire hazards. This project improves safety in homes, industries, and public places while reducing human risk during fire accidents.
\end{joblong}

\begin{joblong}{ALC-LOCK PROTOCOL (ALCOHOL-LOCK) (GitHub)}{Jan 2026 -- Present}
\item The Alcohol Sensing Alert with Engine Locking System is a safety-based embedded system designed to detect alcohol levels from the driver's breath and prevent vehicle operation when the alcohol level exceeds a predefined threshold. The system helps reduce accidents caused by drunk driving by automatically disabling vehicle ignition.
\end{joblong}

\begin{joblong}{EXHALED AMMONIA MONITORING SYSTEM (EAMS) (GitHub)}{Apr 2026 -- Present}
\item The Breathing to Kidney Disease Detection System is a biomedical project that analyzes a person's breath to detect possible kidney dysfunction non-invasively. In kidney disease, higher levels of ammonia and urea-related compounds are present in breath samples. The system uses gas sensors to detect these compounds, providing an early warning mechanism for kidney-related disorders.
\end{joblong}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Academic Details}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    \item B.Tech in Electronics and Communication Engineering, NIST University, Berhampur (2024 -- Present)
    \item Completed 12th Science, Saraswati Sishu Vidya Mandir, Neelakantha Nagar, Berhampur (2021 -- 2023)
    \item Completed 10th BSE, Saraswati Sishu Vidya Mandir, Neelakantha Nagar, Berhampur (2020 -- 2021)
\end{itemize}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Certificates}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    \item Blender Task Completion Certificate
    \item Cisco Course Completion Certificate
    \item Google Arcade Completion Certificate
\end{itemize}

%----------------------------------------------------------------------------------------
%	PERSONAL DETAILS
%----------------------------------------------------------------------------------------
\section{Personal Details}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    \item \textbf{Date of Birth:} 22nd March 2006
    \item \textbf{Hobbies:} Dancing, Reading
    \item \textbf{Extra-Curricular Activities:} Debate, Philosophical Writing
\end{itemize}

\vfill
\center{\footnotesize Last updated: May 6, 2026}

\end{document}
